raptr: Representative and Adequate Prioritisation Toolkit in R

### 2016-09-30 code/rmarkdown/article.Rmd
+ attempts to manipulate refs

## CASE STUDY 2
### Methods
Here we used space-based targets to generate a prioritisation securing a representative sample of a species' intra-specific genetic variation. We used species occurrence and multilocus AFLP data collected by the international IntraBioDiv project in the European Alps [@r462; see @r461 and @r463 for further explanation of data collection]. Although this dataset contains multiple plant species, we used data for the `r tolower(cs2.params.LST[[MODE]]$common.name)` (\textit{`r gsub('_', ' ',cs2.params.LST[[MODE]]$species.name,fixed=TRUE)`}), a wide-spread species with significant genetic structure [@r454] as a simple case study. Members of the IntraBioDiv project collected data using a $20^{\prime}$ longitude by $21^{\prime}$ latitude grid (approx. 22.3 km $\times$ 25 km; Fig. 7a). They visited every second grid cell, and if the `r tolower(cs2.params.LST[[MODE]]$common.name)` was detected in a cell, samples were collected from three individuals. Samples were genotyped using amplified fragment length polymorphisms [AFLP; @r453], and used to construct matrices denoting the presence/absence of polymorphisms at loci. In total, `r structurer::n.samples(cs2.spp.StructureData.LST[[1]])` individuals were genotyped at `r structurer::n.loci(cs2.spp.StructureData.LST[[1]])` markers.

>>>>

## CASE STUDY 2
### Methods
Here we used space-based targets to generate a prioritisation securing a representative sample of a species' intra-specific genetic variation. We used species occurrence and multilocus AFLP data collected by the international IntraBioDiv project in the European Alps [@r463; @r461; @r462]. Although this dataset contains multiple plant species, we used data for the `r tolower(cs2.params.LST[[MODE]]$common.name)` (\textit{`r gsub('_', ' ',cs2.params.LST[[MODE]]$species.name,fixed=TRUE)`}), a wide-spread species with significant genetic structure [@r462] as a simple case study. Members of the IntraBioDiv project collected data using a $20^{\prime}$ longitude by $21^{\prime}$ latitude grid (approx. 22.3 km $\times$ 25 km; Fig. 7a). They visited every second grid cell, and if the `r tolower(cs2.params.LST[[MODE]]$common.name)` was detected in a cell, samples were collected from three individuals. Samples were genotyped using amplified fragment length polymorphisms [AFLP; @r472], and used to construct matrices denoting the presence/absence of polymorphisms at loci. In total, `r structurer::n.samples(cs2.spp.StructureData.LST[[1]])` individuals were genotyped at `r structurer::n.loci(cs2.spp.StructureData.LST[[1]])` markers.
